Creating Venn diagrams

### 2020-05-15 Scripts_for_results/02_creating_lineplot_of_balanced_accuracies.Rmd
added panel spacing
edits

@@

>>>>

```{r}
all_rfperfs <- rbind.data.frame(badata_k562_10kb)
all_rfperfs$CL <- rep("K562", length(badata_k562_10kb))
all_rfperfs$Resolution <- rep("10 kb", length(badata_k562_10kb))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

@@

```{r}
t_whole_arrowhead_gm12878 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/WHOLE/rus/distance/TADRF_3.rds")
t_whole_arrowhead_gm12878 <- t_whole_arrowhead_gm12878[[3]][10,2]
t_whole_arrowhead_k562 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/K562/5kb/results_by_chr/WHOLE/rus/distance/TADRF_3.rds")
t_whole_arrowhead_k562 <- t_whole_arrowhead_k562[[3]][10,2]

t_whole_peakachu_gm12878 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/GM12878/10kb/results_by_chr/WHOLE/rus/distance/TADRF_3_peakachu.rds")
t_whole_peakachu_gm12878 <- t_whole_peakachu_gm12878[[3]][10,2]
t_whole_peakachu_k562 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/K562/10kb/results_by_chr/WHOLE/rus/distance/TADRF_3_peakachu.rds")
t_whole_peakachu_k562 <- t_whole_peakachu_k562[[3]][10,2]

t_chr_arrowhead_gm12878 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_ba_arrowhead_gm12878.rds")
t_chr_arrowhead_k562 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_ba_arrowhead_k562.rds")
t_chr_peakachu_gm12878 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_ba_peakachu_gm12878.rds")
t_chr_peakachu_k562 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_ba_peakachu_k562.rds")

all_rfperfs_chr_vs_whole_arrowhead_peakachu <- data.frame(BA=c(t_whole_arrowhead_gm12878,
                      t_whole_arrowhead_k562,
					  t_whole_peakachu_gm12878,
					  t_whole_peakachu_k562,
					  as.numeric(t_chr_arrowhead_gm12878[12,4]),
					  as.numeric(t_chr_arrowhead_k562[12,4]),
					  as.numeric(t_chr_peakachu_gm12878[12,4]),
					  as.numeric(t_chr_peakachu_k562[12,4])),
				CL=rep(c("GM12878","K562"),4),
				Tool=rep(c("ARROWHEAD","ARROWHEAD","PEAKACHU","PEAKACHU"),2),
				Method=c(rep("Whole",4),rep("Per CHR",4)))

#all_rfperfs_chr_vs_whole_arrowhead_peakachu <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_chr_vs_whole_arrowhead_peakachu.rds")

ggplot(all_rfperfs_chr_vs_whole_arrowhead_peakachu, 
       aes(x=Method, y=BA, fill=Method)) +
  geom_bar(stat = "identity")+
  facet_grid(CL ~ Tool)+
  theme_minimal() +
  theme_bw()+
  xlab("Method") + 
  ylab("Balanced Accuracy") + 
  guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  #panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")
```

### 2020-05-15 Scripts_for_results/04_creating_rfe_lineplot.Rmd
edits

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

>>>>

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,4:5)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}
rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
                   PerformanceSD = sd(BA, na.rm = TRUE))

@@

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,4:5)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}
rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
                   PerformanceSD = sd(BA, na.rm = TRUE))

### 2020-05-15 Scripts_for_results/06_creating_enriched_heatmaps.Rmd
edits

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

>>>>

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

### 2020-05-15 Scripts_for_results/07_creating_distance_to_chipseq.Rmd
edits

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

>>>>

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

### 2020-05-15 Scripts_for_results/08_creating_venn_diagrams.Rmd
edits

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

@@

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

@@

>>>>

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

@@

all_true_bounds_gm12878 <- flank(all_true_bounds_gm12878, 10000, both=TRUE)
all_pred_bounds_gm12878 <- flank(all_pred_bounds_gm12878, 10000, both=TRUE)

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

@@

all_true_bounds_k562 <- flank(all_true_bounds_k562, 10000, both=TRUE)
all_pred_bounds_k562 <- flank(all_pred_bounds_k562, 10000, both=TRUE)
